koda: Deep Learning-Enhanced Pipeline for Keyword Detection in Document Images

### 2020-01-15 paper/paper.tex
Add hyperlinks

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage[margin=3cm]{geometry}
\usepackage{titlesec}

@@

\begin{abstract}
This paper proposes a pipeline, KODA, suitable for keyword highlighting in document images. At its core, KODA uses a combination of edge detection, hough transform, OCR and warping to achieve the result. The study describes the custom, deep learning-based, approach for edge detection, motivated by the problems of traditional techniques and explaining the model training process, along with examples. Moreover, document detection and warping algorithms are detailed, as well as the keyword highlighting process.
\end{abstract}

\begingroup\let\clearpage\relax
\vspace{2cm}
\tableofcontents \endgroup

@@

The implementation to find the intersection relies on \footnote{ \texttt{numpy.linalg.solve}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.solve.html} which may raises an exception if the A matrix is singular because the computation is not possible. Whenever this happens, a least square solution, if it converges, via \footnote{\texttt{numpy.linalg.lstsq}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.lstsq.html} is provided.

>>>>

\usepackage{graphicx}
\usepackage{float}
\usepackage{amsmath}
\usepackage[margin=3cm]{geometry}
\usepackage{titlesec}
\usepackage{hyperref}

@@

\begin{abstract}
This paper proposes a pipeline, KODA, suitable for keyword highlighting in document images. At its core, KODA uses a combination of edge detection, hough transform, OCR and warping to achieve the result. The study describes the custom, deep learning-based, approach for edge detection, motivated by the problems of traditional techniques and explaining the model training process, along with examples. Moreover, document detection and warping algorithms are detailed, as well as the keyword highlighting process.

\vspace{1cm}
All the code can be found in the repository: \url{https://github.com/federico-terzi/koda}
\end{abstract}

\begingroup\let\clearpage\relax
\vspace{1cm}
\tableofcontents \endgroup

@@

The implementation to find the intersection relies on \texttt{numpy.linalg.solve}\footnote{ \texttt{numpy.linalg.solve}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.solve.html} which may raises an exception if the A matrix is singular because the computation is not possible. Whenever this happens, a least square solution, if it converges, via \texttt{numpy.linalg.lstsq} \footnote{\texttt{numpy.linalg.lstsq}: https://docs.scipy.org/doc/numpy/reference/generated/numpy.linalg.lstsq.html} is provided.
